\chapter{Test}
\begin{center}
    \begin{longtable}[htbp]{| p{27mm} | l | p{27mm} | p{27mm} | p{27mm} |}
        \hline
        \textbf{Risk} & \textbf{E(r)} & \textbf{Mitigation} & \textbf{Monitoring} & \textbf{Management} \\ 
        \hline
        Unrealistic \newline project scope & 6 & Have good \newline communication \newline with our \newline supervisor about \newline a realistic project \newline scope & Regularly ask \newline supervisor about project scope & Seek \newline consultation from our \newline supervisor \\
        \hline
        Extended time \newline spent on \newline research & 4 & Assign different topics to each group member & Regularly ask supervisor about level of understanding. & Consider adjusting project scope. \\
        \hline
        Inter group \newline disagreement & 2.7 & Democratic \newline decisions & Have regular \newline meetings and \newline document \newline decisions & Consult semester coordinator \\
        \hline
        Lack of \newline experience with \newline machine intelligence. & 1.5 & Remember knowledge sharing in group. & Discuss understanding of theory at supervisor meetings. & Simplify importance of machine intelligence. Rework design process. \\
        \hline
        Group members leaving the group & 1.5 & Be supportive of each other both in project and courses. & Have regular \newline group meetings. & Adjust project \newline scope if necessary. Rework project schedule. \\
        \hline
        Server goes \newline down & 1.2 & Peer review on \newline code before \newline upload to server & Communicate \newline with the server \newline group about the \newline server status & Wait for server \newline group to setup \newline server \\
        \hline
        Technical debt \newline from legacy code & 1.2 & Limit \newline dependencies from legacy code & Reviewing legacy code & Rewrite code \newline or remove\newline dependency \\
        \hline
        Extended \newline absence of group \newline members & 1.2 & Have a good\newline group\newline environment and encourage daily communication and participation & Monitoring attendance & Talk to the group members and \newline supervisor \\
        \hline
        Lack of experience with servers & 1.2 & Knowledge sharing with server group. & Discuss level of understanding with supervisor and server group. & Consult semester coordinator. \\
        \hline
        \caption{Risk management plan.}
    \end{longtable}
\end{center}