\FloatBarrier
\oldsection*{Tools}
The tools we used to collaborate are not that different from previous \gls{astep} groups as we took their advice on many of them.

\subsection*{Communication}
Most of the communication was organized on discord. Communication through discord proved beneficial when COVID-19 restrictions send everyone home. Discord has a proper voice channel implementation, and we used this tool in four areas for collaboration.
 
\begin{itemize}
     \item Supervisor meetings
     \item Group discussions
     \item Server group Collaborations
     \item Super group meetings
\end{itemize}

\subsection*{Version control}
Just as the \gls{astep} groups before us, we used the \gls{gitlab} server as a version control system. It now contains code from 2016 to 2020, and serves as shared repository for legacy services and archival of source code.

\Gls{gitlab} is set up with \gls{cicd} using a build server and a \gls{kubernetes} cluster. It works out of the box with simple hello world projects. We found this combination encourages collaboration between groups as we are developing for \gls{astep} on a shared platform.

\subsection*{Deployment}
We kept the \gls{kubernetes} servers as they seem to work well. It allows us to integrate with \gls{gitlab} and perform \gls{cicd}, besides a few updates and configuration changes it works largely the same, we found this made collaboration easy as a recent version was always live on \gls{astep} for testing. Collaborating when maintaining \gls{kubernetes} was easy as multiple users could use their login to control \gls{kubernetes} simultaneously.
