Supervisor meeting 3/3 13:14

Attendies:

Kristian V
Kristian O
Jonas
Jeppe
Rasmus

Tung

Location: Meeting was held in group room

Mathias leaves the group (changes semester). We dont know if we need to do something. Tung says we cannot do anything, and even if he has a conflict with us we cannot do anything since he changes semester.

We sent you our report. Tung sent a very good report for us in return. Tung says our report is too short and not good for submit. Kristian says the guidelines of 60 pages was our concern.  Tung wants more explaintion in particular a better RISK definition, with risk value and prioritied list. We should create a plan and prioritze the tasks in the plan. 

Tung says we can use public data on outlier detection, and asks if we still want to use it, we can either have a simple outlier detection or complicated outlier detection. We choose complicated. Tung wants to send us a paper we should read regarding this. We should have a plan and impliment it like the group he sent us did it.

Our Task:
1. Read report he sent to understand the flow
2. Read scientific report he sent us.

It is okay to exceed the page limit by 10 pages

Should we include our "team work" that we did in the project? Tung says yes and afterwards we can filter and remove uneeded. Tung says we cheat examinator ;)

Tung says the last group he supervises, wrote report on UI/UX when they did teamwork with another group. 

Kristian asks how our UI could look? Tung draws a graph and talks about a blue curve. We have to meet with the other time series group and work common, and tung thinks it is good idea.

what is the format of the data? is 3 colum data good? 
Value | Timestamp | outlierbool

Tung suggest:
timestamp | temp | rainfall | etc. | 

But how can we then annotate the outlier?
Tung says we usually say all the data points are outliers regardless of the other values. 

when we have outlier the patient has a heartattack the the other data values at that time is still outlier even if they are "common".

Tung asks when we will send next paper/have next meeting. Next week, we will send an email, tung says okay and leaves.